### 2017-05-03 R/ITHIM.Rmd
Fixed a bug in GBDList creation

GBD <- with(GBD, data.frame(state, disease, sex, ageClass, variable, value, stringsAsFactors = FALSE)) %>% arrange(state,disease,sex,ageClass,variable)

@@

```{r statewiseGBD, eval = TRUE, dev=c('pdf', 'png'), fig.width = 2*fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}
D <- melt(lapply(ITHIMList, function(ITHIM) return(ITHIM@parameters@GBD)))
names(D) <- c("disease","sex","ageClass","type", "burden", "sex2", "disease2", "state")

@@

```{r displayMeans, eval = FALSE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = phi, warning = FALSE, message = FALSE, echo = FALSE}

>>>>

GBD <- with(GBD, data.frame(state, disease, sex, ageClass, burdenType = variable, value, stringsAsFactors = FALSE)) %>% arrange(state,disease,sex,ageClass,burdenType)

@@

```{r statewiseGBD, eval = FALSE, dev=c('pdf', 'png'), fig.width = 2*fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}
D <- melt(lapply(ITHIMList, function(ITHIM) return(ITHIM@parameters@GBD)))

D <- do.call(rbind,lapply(ITHIMList, getGBD))

names(D) <- c("disease","sex","ageClass","type", "burden", "sex2", "disease2", "state")

@@

```{r displayMeans, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = phi, warning = FALSE, message = FALSE, echo = FALSE}
